Community-based marine reserves in Mexico: do they work?

### 2018-02-27 GainesLabPresentation.Rmd
small changes to presentation

- Operationalization of the social-ecological systems framework (Gracias Ere!)

@@

@@

- Should be the perfect example... but

- Has had mass mortality events due to hypoxia (2009, 2010) and warm water (~2015)

@@

@@

@@

>>>>

- Operationalization of the social-ecological systems framework
  - (Gracias Ere!)

@@

- Should be the perfect example:

@@

- But:

  - Mortality events due to hypoxia (2009, 2010) and warm water (~2015)

@@

- This is:

@@

- But not a great design:

@@

- Opposite to Isla Natividad:

- But:
